Bayesian Inference from Time Series: Information Loss and the Whittle Likelihood

### 2018-03-05 doc/ms.tex
More writing

\title{Bayesian inference from time series: Information loss and the Whittle likelihood}
\author{Brendon J. Brewer}
\date{2018}

@@

We assume that the probability distribution for $\epsilon(t)$ is indeed white
noise. In this case, the probability distribution for $y(t)$ given the
parameters is a gaussian process with mean function of zero and
covariance function given by
\begin{align}
C(\tau) &= A^2\left[\cos(\eta\omega_0\tau)
                + \frac{1}{2\eta Q}\sin(\eta\omega_0\tau)\right]
\end{align}
where $\eta = \sqrt{|1 - 1/(4Q^2)|}$, $\tau$ is a time separation,
and $Q > 1/2$ (i.e., we assume the oscillation is not overdamped).
An equivalent expression is given by \citet{anderson} and
\citet{celerite}.

@@

\begin{thebibliography}{999}
\bibitem[Anderson et al.(1990)]{anderson}
Anderson, Edwin R., Thomas L. Duvall Jr, and Stuart M. Jefferies. "Modeling of solar oscillation power spectra." The Astrophysical Journal 364 (1990): 699-705.

>>>>

\title{Bayesian Inference from Time Series: Information Loss and the Whittle Likelihood}
\author{Brendon J. Brewer}
\date{2018}

@@

We assume that the probability distribution for $\epsilon(t)$ is indeed white
noise. In this case, the probability distribution for $y(t)$ given the
parameters is a gaussian process with mean function of zero and
covariance function given by
\begin{align}
C(\tau) &= A^2\left[\cos(\eta\omega_0\tau)
                + \frac{1}{2\eta Q}\sin(\eta\omega_0\tau)\right]
\end{align}
where $\eta = \sqrt{1 - 1/(4Q^2)}$, $\tau$ is a time separation,
and $Q > 1/2$ (i.e., we assume the oscillation is not overdamped).
A more general expression which allows for $Q \leq 1/2$
is given by \citet{anderson} and \citet{celerite}.
In the limit of large $Q$, the covariance function is approximately
the product of an oscillation and an exponential decay:
\begin{align}
C(\tau) &= A\exp\left(-\frac{\omega_0\tau}{2Q}\right)\cos(\omega_0\tau)
\end{align}
which was the form assumed by \citep{brewer_stello}.

@@

\begin{thebibliography}{999}
\bibitem[Anderson et al.(1990)]{anderson}
Anderson, Edwin R., Thomas L. Duvall Jr, and Stuart M. Jefferies. ``Modeling of solar oscillation power spectra.'' The Astrophysical Journal 364 (1990): 699-705.

\bibitem[Brewer and Stello(2009)]{brewer_stello}
Brewer, Brendon J., and Dennis Stello. ``Gaussian process modelling of asteroseismic data.'' Monthly Notices of the Royal Astronomical Society 395, no. 4 (2009): 2226-2233.
